Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-04 02_Paper/paper.tex
updates some grammar check - update table 4

Whenever a QC method is selected, it is important to remark that compromises must be made in most cases. For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the

@@

This paper is divided in 6 sections:

\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Industrial projects requires to work with a variety of sensors and controllers. Thus, it might occurs incompatibility between technologies. In order to avoid that problem, universal protocols are often implemented at industrial projects. This is the case for our industrial 4.0 demonstration cell, which shares data via protocol OPC-UA.

Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell. For our case, the data is shared independently from two OPC-UA servers. This in order to represent the interaction between multiple servers in real production environments.

The first step to collect the data is to list all the variables of interest and to map their source. The second step is to determine the use cases of interest.  On this research, we focussed on the data described on Table.~\ref{tab:data_source} and the six use cases described on Table.~\ref{tab:use_cases}. The data was manually collected by using the software "UAExperts". Approximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.

\begin{table}
       \centering
       \begin{adjustbox}{width=.45\textwidth}
       \begin{tabular}{ c c c } \toprule
              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Conveyor: Gate
                     \item Conveyor: QC
                     \item Conveyor: Store
                     \end{description}
                     \end{minipage} \\ \hline
              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item $xyz$ Gripper position
                     \end{description}
                     \end{minipage} \\ \hline
              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item UR3 gripper open/close
                     \item Grab/drop disk based on disk type
                     \end{description}
                     \end{minipage} \\ \hline
              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item OK-NOK label
                     \item $xy$ disk deviation from the center point
                     \item Absolute disk deviation
                     \end{description}
                     \end{minipage} \\ \hline
              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Position
                     \item Speed
                     \item Safe to go
                     \end{description}
                     \end{minipage} \\ \hline
              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     \begin{description}
                     \item Disk Size
                     \end{description}
                   \end{minipage} \\ \bottomrule
       \end{tabular}
       \end{adjustbox}
       \caption{Industriy 4.0 demonstration cell: Relevant data with its reference source server}
       \label{tab:data_source}
\end{table}

@@

\begin{figure}
       \includegraphics[width=.45\textwidth]{img/demozelle_conex_diagram.png}
       \caption{Industry 4.0 demostration cell: Connection diagram (simplified)
             }
\label{fig:demo_conn_diag}
\end{figure}

@@

\begin{table}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $8$ & $24$ & $8+24 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+8 = 26$} & \multicolumn{    1}{c}{$0+24 = 24$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{SVM.}
              \label{tab:SVM_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $6$ & $26$ & $6+26 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+6 = 24$} & \multicolumn{    1}{c}{$0+26 = 26$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{MLP.}
              \label{tab:MPL_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $17$ & $1$ & $17+1 = 18$\\
                     \cline{2-4}
                     & NOK & $0$ & $32$ & $0+32 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$17+0 = 17$} & \multicolumn{    1}{c}{$1+32 = 33$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Decision Tree.}
              \label{tab:Tree_conf_matrix}
       \end{subtable}
       \caption{Confusion matrix result of the prediction of 50 data-points.}
       \label{tab:Confusion_matrix}
\end{table}

@@

\bibliographystyle{ieeetr} %elsarticle-harv} %abbrv
\bibliography{bib}

>>>>

Whenever a QC method is selected, it is important to remark that compromises must be made in most cases. For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the \AP{review}

@@

This paper is divided in 6 sections:
\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Industrial projects require to work with a variety of sensors and controllers. Thus, might occur incompatibility between technologies. To avoid that problem, universal protocols are often implemented at industrial projects. This is the case for our industrial 4.0 demonstration cell, which shares data via protocol OPC-UA.

Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell. For our case, the data is shared independently from two OPC-UA servers. This represents the interaction between multiple servers in real production environments.

The first step to collect the data is to list all the variables of interest and to map their source. The second step is to determine the use cases of interest.  This research focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}. The data was manually collected by using the software "UAExperts". Approximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.

\begin{table}
       \centering
       \begin{adjustbox}{width=.45\textwidth}
       \begin{tabular}{ c c c } \toprule
              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Conveyor: Gate
                     \item Conveyor: QC
                     \item Conveyor: Store
                     \end{description}
                     \end{minipage} \\ \hline
              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item $xyz$ Gripper position
                     \end{description}
                     \end{minipage} \\ \hline
              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item UR3 gripper open/close
                     \item Grab/drop disk based on disk type
                     \end{description}
                     \end{minipage} \\ \hline
              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item OK-NOK label
                     \item $xy$ disk deviation from the center point
                     \item Absolute disk deviation
                     \end{description}
                     \end{minipage} \\ \hline
              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
              \begin{description}
                     \item Position
                     \item Speed
                     \item Safe to go
                     \end{description}
                     \end{minipage} \\ \hline
              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                     \begin{description}
                     \item Disk Size
                     \end{description}
                   \end{minipage} \\ \bottomrule
       \end{tabular}
       \end{adjustbox}
       \caption{Industriy 4.0 demonstration cell: Relevant data linked with its reference source server.}
       \label{tab:data_source}
\end{table}

@@

\begin{figure}
       \includegraphics[width=.45\textwidth]{img/demozelle_conex_diagram.png}
       \caption{Industry 4.0 demostration cell: Connection diagram (simplified).
             }
\label{fig:demo_conn_diag}
\end{figure}

@@

\begin{table}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $8$ & $24$ & $8+24 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+8 = 26$} & \multicolumn{    1}{c}{$0+24 = 24$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Support Vector Machine.}
              \label{tab:SVM_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
                     \cline{2-4}
                     & NOK & $6$ & $26$ & $6+26 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+6 = 24$} & \multicolumn{    1}{c}{$0+26 = 26$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Multilayer Perceptron.}
              \label{tab:MPL_conf_matrix}
       \end{subtable}
       \begin{subtable}[h]{0.3\textwidth}
              \centering
              \begin{adjustbox}{width=1.6\textwidth}
              \begin{tabular}{l|l|c|c|c}
                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
                     \cline{3-4}
                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
                     \cline{2-4}
                     \multirow{2}{*}{Predicted Values}& OK & $17$ & $1$ & $17+1 = 18$\\
                     \cline{2-4}
                     & NOK & $0$ & $32$ & $0+32 = 32$\\
                     \cline{2-4}
                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$17+0 = 17$} & \multicolumn{    1}{c}{$1+32 = 33$} & \multicolumn{1}{c}{$50$}\\
              \end{tabular}
              \end{adjustbox}
              \caption{Decision Tree.}
              \label{tab:Tree_conf_matrix}
       \end{subtable}
       \caption{Confusion matrices result of the prediction of 50 test data-points. We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs and predictions. The tables read from the upper left cell as: true-positive, false-positive, false-negative, true-negative.}
       \label{tab:Confusion_matrix}
\end{table}

@@

\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv
\bibliography{bib}
